\chapter{LITERATURE REVIEW }

\section{Working of Existing System: }
In the present system all work is done on paper. The whole session attendance is stored in register and at the end of the session the reports are generated. We are not interested in generating report in the middle of the session or as per the requirement because it takes more time in calculation. At the end of session the students who don’t have 75 \% attendance get a notice. The second method is finger print recognition. But for some people it is intrusive, because it is still related to criminal identification. Another disadvantage of finger print recognition is that it can make mistakes with the dryness or dirt of the fingers skin. There are various methods for facial recognition like eigenface method. Various extensions have been made to the eigenface method such eigenfeatures.\cite{sups} This method combines facial metrics (measuring distance between facial features) with the eigenface representation. Another method similar to the eigenface technique is 'fisher faces' which uses Linear discriminate analysis This method for facial recognition is less sensitive to variation in lighting and pose of the face than using eigenfaces. Fisher face utilizes labeled data to retain more of the class specific information during the dimension reduction stage. A further alternative to eigenfaces and fisherfaces is the active appearance model. This approach uses an Active Shape Model to describe the outline of a face. By collecting many face outlines, Principal Component Analysis can be used to form a basis set of models which, encapsulate the variation of different faces. Many modern approaches still use Principal Component Analysis as a means of dimension reduction or to form basis images for different modes of variation.\cite{pdya}

\newpage
\subsection{Disadvantages of Present Working System: }
\begin{itemize}
 \item       Not User Friendly 
 \item       Difficulty in report generation 
 \item        Manual control
 \item        Lots of paper work 
 \item        Time consuming 
\end{itemize}
        
\section{Proposed Plan of Work: }
This Application is built for automating the processing of attendance. It also enhances the speed of the performing attendance task easily. It also generates periodic reports to keep a check on the students who are regular \& who are not. So that creates this application In that Different modules are created. The first module is registration part enter the information of student in that roll number, name, year, semester, password \&  store in to database. Then second module is login part in that enter the roll number \& password then click on login button it open automatically camera through opencv manager. Third module is marking attendance in that enter the roll number, subject name, date \& password then click on make attendance button it automatically open camera \& take face it detect face, recognition the face mark the attendance then give the remark of the student and store in to database. The last module is get report in that enter the subject name and date \& click on the get report button it gives the report of particular report of the subject. A Faculty has to login to the system \& then in the attendance option they have to select appropriate class, semester and subject. So this will display the list of the students who are eligible to appear in this session. So now the faculty has to just select the students name from the manual attendance sheet according to their roll number and then submit the sheet. This will add the selected students as present student in that particular session. This system is very useful to the office staff also because, they can generate various types of reports and submit them to respective faculties also or also can be submitted to the College Coordinator. \cite{manju}

\newpage
\subsection{Characteristics of Proposed System:}
1) User Friendly: 
The proposed system is user friendly because the retrieval and storing of data is fast and data is maintained efficiently. Moreover the graphical user interface is provided in the proposed system, which provides user to deal with the system very easily. 

2) Reports are easily generated: 
reports can be easily generated in the proposed system so user can generate the report as per the requirement (monthly) or in the middle of the session. User can give the notice to the students so he/she become regular.

3) Very less paper work:
 The proposed system requires very less paper work. All the data is feted into the computer immediately and reports can be generated through computers. Moreover work becomes very easy because there is no need to keep data on papers.

4) Computer operator control:
 Computer operator control will be there so no chance of errors. Moreover storing and retrieving of information is easy. So work can be done speedily and in time.




