\chapter{OBJECTIVE AND SCOPE}
\section{Problem Statement: }

Every time a lecture, section or laboratory starts the lecturer or teaching Assistant delays the lecture to record students’ attendance. This is a lengthy process and takes lot of time and effort, especially if it is a lecture with huge number of students. It also causes a lot of disturbance and interruption when an exam is held. Moreover the attendance sheet is subjected to damage and loss while being passed on between different students of teaching staff. And when the number of students enrolled in a certain course is huge, the lecturers tend to call a couple of students name at random which is not fair student evaluation process either. Finally, these attendance records are used by the staff to monitor the student’s attendance rates. This process could be easy and effective with a small number of students but on the other hand dealing with the records of a large number of students often leads to human error. \cite{priti}

\section{Objective: }
Attendance Monitoring System (AMS) can be made into smarter way by using face recognition technique, to captures the image of the person and checks the observed image with the face database using android enhanced smart phone \& to store in canter database.
It is typically used for two purposes. Firstly, marking attendance for student by comparing the face images produced recently and secondly, recognition of human who are strange to the environment i.e. an unauthorized person. For matching the captured images with the database, opencv libraries methodology was used.\cite{pdya} 
\newpage
\begin{itemize}
     \item    Simplified attendance with respect to traditional method 
     \item    Gallery images must be of same size.
      \item   Requires full frontal face to be presented for each time.
      \item    To provide paperless environment by using computerize system that can save lot of time. 
    \item      No need to maintain several separate records and mannual calculation.
\end{itemize}
           
\section{Scope: }
	This project is basically an android application which means self contained software runs on the system on which it has been installed under the user control and it will work for a particular institute or college only.

\section{Out of Scope: }	
\begin{itemize}
     \item         It only take attendance and make the report.
     \item         We not providing the automatic SMS facility for defaulters.
     \end{itemize}


