\chapter{REQUIREMENT ANALYSIS}

\section{Software Requirements: }
\subsection{Software requirement while developing system: }
\begin{itemize}
\item Operating System  - Windows XP or Windows 7
\item Database- MySQL
\item Technologies- JAVA ,Android,PHP
\item IDE- Eclipse kepler,SDK,JDK 7,OpenCV SDK
\end{itemize}

\subsection{Software requirement while using system: }
\begin{itemize}
\item Android OS
\end{itemize}

\section{Hardware Requirements: }
\subsection{Hardware requirement while developing system: }
\begin{itemize}
\item PC/Laptop
\end{itemize}

\subsection{Hardware requirement while using system: }
\begin{itemize}
\item Tablet/Mobile of android platform
\end{itemize}

\section{Required softwares: }

\subsection{Android Operating System: }
 Android is a mobile operating system (OS) based on the Linux kernel and currently developed by Google OHA. With a user interface based on direct manipulation, Android is designed primarily for touch screen mobile devices such as smart phones and tablet computers, with specialized user interfaces for televisions (Android TV), cars (Android Auto), and wrist watches (Android Wear). The OS uses touch inputs that loosely correspond to real-world actions, like swiping, tapping, pinching, and reverse pinching to 
manipulate on-screen objects, and a virtual keyboard.

Android is the most popular mobile OS. As of 2013, Android devices sell more than Windows and Mac OS devices combined, with sales in 2012, 2013 and 2014 close to the installed base of all PCs.. A developer survey conducted in April–May 2013 found that 71\% of mobile developers develop for Android. At Google I/O 2014, the company revealed that there were over 1 billion active monthly Android users (that have been active for 30 days), up from 538 million in June 2013.

Android's source code is released by Google under open source licenses, although most Android devices ultimately ship with a combination of open source and proprietary software. Initially developed by Android, Inc., which Google backed financially and later bought in 2005, Android was unveiled in 2007.The Android’s Initial release is in September 23, 2008 and the latest release is in the 4.4.4 Kit Kat / June 19, 2014. The first release of android is Alpha (1.0). 

\subsection{Eclipse: }
In computer programming, Eclipse is an integrated development environment (IDE). It is developed by Eclipse Foundation. The stable release is Stable release 4.4.1 (Luna) / 26 September 2014. It contains a base workspace and an extensible plug-in system for customizing the environment. Written mostly in Java, Eclipse can be used to develop applications. By means of various plug-INS, eclipse may also be used to develop applications in other programming languages: Ada, ABAP, C, C++, COBOL, Fortran, Haskell, JavaScript, Lasso, Natural, Perl, PHP, Prolog, Python, R, Ruby (including Ruby on Rails framework), Scala, Clojure, Groovy, Scheme, and Erlang. It can also be used to develop packages for the software Mathematical. Development environments include the Eclipse Java development tools (JDT) for Java and Scala, Eclipse CDT for C/C++ and Eclipse PDT for PHP, among others.
The initial codebase originated from IBM Visual Age. The Eclipse software development kit (SDK), which includes the Java development tools, is meant for Java developers. Users can extend its abilities by installing plug-ins written for the Eclipse Platform, such as development toolkits for other programming languages, and can write and contribute their own plug-in modules.

\subsection{JDK :}
The Java Development Kit (JDK) is an implementation of either one of the Java SE, Java EE or Java ME platforms released by Oracle Corporation in the form of a binary product aimed at Java developers on Solaris, Linux, Mac OS X or Windows. The JDK includes a private JVM and a few other resources to finish the recipe to a Java Application. Since the introduction of the Java platform, it has been by far the most widely used Software Development Kit (SDK).[citation needed] On 17 November 2006, Sun announced that it would be released under the GNU General Public License (GPL), thus making it free software. This happened in large part on 8 May 2007, when Sun contributed the source code to the OpenJDK.

\subsection{SDK: }
The Android Software Development Kit (Android SDK) contains the necessary tools to create, compile and package Android applications. Most of these tools are command line based. The primary way to develop Android applications is based on the Java programming language. A software development kit (SDK) is typically a set of software development tools that allows the creation of applications for a certain software package, software framework, hardware platform, computer system, video game console, operating system, or similar development platform. It may be something as simple as the implementation of one or more application programming interfaces (APIs) in the form of some libraries to interface to a particular programming language or to include sophisticated hardware that can communicate with a particular embedded system. Common tools include debugging facilities and other utilities, often presented in an integrated development environment (IDE). SDKs also frequently include sample code and supporting technical notes or other supporting documentation to help clarify points made by the primary reference material.
 
\subsection{PHP :}
 PHP is a server-side scripting language designed for web development but also used as a general-purpose programming language. PHP code can be simply mixed with HTML code, or it can be used in combination with various templates engines and web frameworks. PHP code is usually processed by a PHP interpreter, which is usually implemented as a web server's native module or a Common Gateway Interface (CGI) executable. After the PHP code is interpreted and executed, the web server sends resulting output to its client, usually in form of a part of the generated web page; for example, PHP code can generate a web page's HTML code, an image, or some other data. PHP has also evolved to include a command-line interface (CLI) capability and can be used in standalone graphical applications.

We are using a central database means that use the database online anytime or anywhere. For this accessing database use the free web hosting area website. In that use the php language for database design. PHP can generate dynamic page content and it can create, open, read, write, delete, and close files on the server. Also it can collect form data, send and receive cookies and add, delete, modify data in your database and can be used to control user-access PHP and encrypt data with PHP, you are not limited to output HTML. You can output images, PDF files, and even flash movies. You can also output any text, such as XHTML and XML. PHP runs on various platforms (Windows, Linux, UNIX, Mac OS X, etc.)PHP is compatible with almost all servers used today (Apache, IIS, etc.).It supports a wide range of database PHP is free. 











